---
title: "Learning Spatial Stats: Day One "
author: "Rose Martinez"
date: '`r Sys.Date()`'
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

## Reading 
### "Analyzing spatio-temporal data with R: Everything you always wanted to know – but were afraid to ask"

Beginning my spatial statistical learning by reading [Analyzing spatio-temporal data with R: Everything you always wanted to know – but were afraid to ask](https://www.researchgate.net/publication/320223143_Analyzing_spatio-temporal_data_with_R_Everything_you_always_wanted_to_know_-_but_were_afraid_to_ask)

You can embed an R code chunk like this:

```{r cars}
summary(cars)
fit <- lm(dist ~ speed, data = cars)
fit
```

# Including Plots

You can also embed plots. See Figure \@ref(fig:pie) for example:

```{r pie, fig.cap='A fancy pie chart.', tidy=FALSE}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```
